Revisiting the Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation using complex Empirical Orthogonal Functions

### 2021-09-08 analysis/paper/shceof.Rmd
Saca mensaje de sf_s2
Render

```{r setup, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE,
  comment = "#>",
  cache.extra = 43,
  cache.path = "../cache/paper/",
  fig.path = "../figures/",
  dpi = 300,
  dev = c("pdf", "png")
)

@@

# There's a bunch of issues with s2 right now
sf::sf_use_s2(FALSE)

>>>>

```{r setup, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE,
  comment = "#>",
  cache.extra = 41,
  cache.path = "../cache/paper/",
  fig.path = "../figures/",
  dpi = 300,
  dev = c("pdf", "png")
)

@@

# There's a bunch of issues with s2 right now
sink <- capture.output(sf::sf_use_s2(FALSE))
